\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-03-19 thesis_template/paper0904.tex
another results push
Minor updates to results

Further data obtained provided insight into the various types of courses students were taking at McMaster University during the fall/winter 2021 semesters \figref{fig:2}. At this time, McMaster University was slowly shifting back to in-person classes due to COVID-19 restrictions being lifted, however, a large majority of courses had been converted to hybrid, blended learning, and online courses. 60 participants (40\%) indicated that the majority of courses they were taking were mostly hybrid or blended learning style courses. 28 participants (19\%) indicated most of their courses were back in-person, while only 7 participants (5\%) were enrolled in mostly online courses. 30 participants indicated a balanced mix of all course types. These results highlight the shift from traditional teaching practices towards newer, more innovative educational practices.

@@

>>>>

Further data obtained provided insight into the various types of courses students were taking at McMaster University during the fall/winter 2021 semesters \figref{fig:2}. At this time, McMaster University was slowly shifting back to in-person classes due to COVID-19 restrictions being lifted, however, a large majority of courses had been converted to hybrid, blended learning, and online courses. 60 participants (40\%) indicated that the majority of courses they were taking were mostly hybrid or blended learning style courses. 28 participants (19\%) indicated most of their courses were back in-person, while only 7 participants (5\%) were enrolled in mostly online courses. 30 participants indicated a balanced mix of all course types. These results highlight the shift from traditional teaching practices towards more innovative educational practices.

@@

Students were asked to reflect on their experiences as undergraduate students at McMaster University. Participants responded to two questions regarding how much coursework has emphasized certain aspects of their learning \figref{fig:3}, and how often they have applied their learning in different contexts \figref{fig:4}. 62
